TBA

### 2019-10-11 paper.tex
Minor change to text labels

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/sound_localisation.png}
  \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }
  \label{fig:sound-localisation}
\end{figure}

@@

Assuming the differences are normally spread, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency threshold where the participant could not longer reliably tell the tones apart. 
The threshold is set to contain 75\% of each participant's correct guesses and an example of one participant's threshold can be seen in \todo{put in figure}.
The median of these threshold values can then be used to estimate the frequency difference at which the participant population could no longer tell the difference between two tones and can be used to improve the next interface iteration's frequency profile and increase performance. 
\cref{fig:pitch-thresholds} shows a distribution of the thresholds values for each group, along with the median value. 
The median is used here given the skewed plot and was found to be approximately 0.4 semitones for each group.

@@

The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and tilt directions are plotted against each other. 
A set of box-plots of the pan errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
The results are summarised in \cref{tab:target-results}\todo{tabulate results}.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
  \caption{Boxplots of the median pan and elevation errors for each setting. }
  \label{fig:target-boxplot-error}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
  \caption{Boxplots of the absolute median pan and elevation errors for each setting. }
  \label{fig:target-boxplot-absolute-error}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/fitts_fit.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
  \label{fig:fitts-results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/fitts_ips.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
  \label{fig:fitts-ips}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/sound_localisation.png}
  \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }\label{fig:sound-localisation}
\end{figure}

@@

Assuming the differences are normally spread, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency threshold where the participant could not longer reliably tell the tones apart. 
The threshold is set to contain 75\% of each participant's correct guesses.% and an example of one participant's threshold can be seen in \todo{put in figure}.
The median of these threshold values can then be used to estimate the frequency difference at which the participant population could no longer tell the difference between two tones and can be used to improve the next interface iteration's frequency profile and increase performance. 
\cref{fig:pitch-thresholds} shows a distribution of the thresholds values for each group, along with the median value. 
The median is used here given the skewed plot and was found to be approximately 0.4 semitones for each group.

@@

The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and tilt directions are plotted against each other. 
A set of box-plots of the pan errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
The results are summarised in \cref{tab:target-results}.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
  \caption{Boxplots of the median pan and elevation errors for each setting. }\label{fig:target-boxplot-error}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
  \caption{Boxplots of the absolute median pan and elevation errors for each setting. }\label{fig:target-boxplot-absolute-error}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/fitts_fit.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/fitts_ips.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
\end{figure}
